 

### 2020-11-13 doc/manuscript/Dow_manuscript.Rmd
update hypothesis table, misc cleanup

**Title:** ~~Effect of spring temperatures on tree growth phenology in two temperate deciduous forests~~
Warmer spring temperatures in temperate deciduous forests cause earlier tree growth but have little effect on annual woody productivity

@@

Cameron Dow^1^,
Loïc D’Orangeville,
Erika B. Gonzalez-Akre^1^,
Ryan Helcoski^1^,
Valentine Herrmann^1^,
Ian McGregor^1^,
Sean McMahon,
Albert Kim^1^,
David A. Orwig,
Kristina J. Anderson-Teixeira^1,n^*

@@

```{r eval=FALSE, echo=FALSE}
## This is a chunk that won't be evaluated or displayed. I use these for notes.
## Target journal: ??? Global Change Biology????
## Instructions for authors: 
#[insert guidance on word count, n figures/ tables allowed, and then some rough planning of what goes in this manuscript]

```{r eval = TRUE, echo=FALSE, warning=FALSE, results='hide'}
#Figures & Tables: listing figures and their number here is helpful for planning, and also allows automatic numbering within text -->easy changing of order.

@@

climwin_caption <- "Figure 3. Landscapes of relationships between the day of year on which 25% of annual growth is achieved (DOY_25) and temperature in prior weeks for ring- and diffuse-porous trees at SCBI and Harvard Forest. Shown are matrices of linear coefficients of first-order linear regressions between temperature and DOY_25, where Window Open and Window Close indicate number of weeks prior to DOY_25 (ring-porous: DATE at SCBI, DATE at HF; diffuse-porous: DATE at SCBI, DATE at HF). Black boxes indicate the optimal window."

@@

# Abstract

@@

## (We also know little about differences across species or functional groups, which matters because it will affect how different species fare under climate change )
~~A recent publication by D'Orangeville et al () found that~~ Leaf and wood phenology  traits, along with their apparent relationships, are dissimilar among trees of different wood types (ring-porous and diffuse-porous; **D'Orangeville et al. **). For example, ~~they observed that~~ bud burst occurs around the same time as 25% total annual growth, and 75% leaf development coincided with 50% total annual growth in ring-porous trees, while leaf phenology and stem growth phenology were decoupled in diffuse-porous trees.

@@

## Study sites and data

@@

## Data collection and cleaning
### Dendrometer bands

@@

### Tree-rings
(*tree rings, if included-- KAT can write this*)

@@

## Data analysis
### Fitting growth curves

We fit the model of @mcmahon_general_2015 to define *phenological dates and growth rates* (Fig. `r schematic`).

### Determining optimal climate windows

@@

### Hypothesis testing

@@

# Acknowledgements
people: (everyone who helped collect data), Jess Shue (data), Neil Pederson (helpful discussion) 
Funding: ForestGEO

>>>>

**Title:** Warmer spring temperatures in temperate deciduous forests cause earlier tree growth but have little effect on annual woody productivity

@@

Cameron Dow^1^

Loïc D’Orangeville

Erika B. Gonzalez-Akre^1^

Ryan Helcoski^1^

Valentine Herrmann^1^

Ian McGregor^1^

Sean McMahon

Albert Kim^1^

David A. Orwig

Neil Pederson

Kristina J. Anderson-Teixeira^1,n^*

@@

```{r eval = TRUE, echo=FALSE, warning=FALSE, results='hide'}

## Target journal: Global Change Biology
## Instructions for authors: https://onlinelibrary-wiley-com.smithsonian.idm.oclc.org/page/journal/13652486/homepage/forauthors.html
## Primary Research Articles present the results of a completed research project and are up to 8000 words in length. Word limits apply to the main body of the text (Introduction, Materials and Methods, Results, Discussion, and Acknowledgements).

## I don't think GCB has an official limit. I just saw a recently accepted article with 10 figures and 4 tables, so we're fine!

#Figures & Tables: listing figures and their number here is helpful for planning, and also allows automatic numbering within text -->easy changing of order.

@@

climwin_caption <- "Figure 3. THIS IS OUT OF DATE. Landscapes of relationships between the day of year on which 25% of annual growth is achieved (DOY_25) and temperature in prior weeks for ring- and diffuse-porous trees at SCBI and Harvard Forest. Shown are matrices of linear coefficients of first-order linear regressions between temperature and DOY_25, where Window Open and Window Close indicate number of weeks prior to DOY_25 (ring-porous: DATE at SCBI, DATE at HF; diffuse-porous: DATE at SCBI, DATE at HF). Black boxes indicate the optimal window."

@@

# Abstract
```{r eval=FALSE, echo=FALSE}
## For GCB:
## Abstract limit for GCB is 300 words. 
## 6-10 keywords

@@

## (We also know little about differences across species or functional groups, which matters because it will affect how different species fare under climate change )
Leaf and wood phenology  traits, along with their apparent relationships, are dissimilar among trees of different wood types (ring-porous and diffuse-porous; **D'Orangeville et al. **). For example, bud burst occurs around the same time as 25% total annual growth, and 75% leaf development coincided with 50% total annual growth in ring-porous trees, while leaf phenology and stem growth phenology were decoupled in diffuse-porous trees.

@@

## Study sites

@@

## Data preparation
### Dendrometer bands

@@

We fit the model of @mcmahon_general_2015 to define *phenological dates and growth rates* (Fig. `r schematic`). 
...DETAILS...

After model fitting, we used  a script to remove outliers....

### Tree-rings
(*tree rings-- KAT can write this*)

@@

(*climate data for tree rings-- KAT can write this*)

## (Climwin)

@@

## Hypothesis testing

@@

# Acknowledgements
people: (everyone who helped collect data), Jess Shue (data)
Funding: ForestGEO

### 2020-11-13 doc/manuscript/tables_figures/tables.Rmd
update hypothesis table, misc cleanup

kable(hypothesis_table, col.names = c("Hypotheses and Specific Predictions", "RP", "DP","RP", "DP"), caption = "Table 1. Hypothesis table", format = "latex", booktabs = TRUE,  escape = F)%>%
  #column_spec(1, width = "4cm") %>%
  add_header_above(c(" ", "SCBI" = 2, "Harvard"=2 )) %>%
  pack_rows("1. Warmer early springs result in earlier stem growth and longer growing seasons", 1, 5, latex_gap_space = "1em", colnum = 4, hline_before = FALSE) %>%
  pack_rows("2. Maximum growth rates are independent of early spring temperatures.", 6, 6, latex_gap_space = "1em", colnum = 4, hline_before = FALSE) %>%
  pack_rows("3. Annual stem growth responds positively to warmer spring temperatures.", 7, 8, latex_gap_space = "1em", colnum = 4, hline_before = FALSE) %>%
  kable_styling(latex_options = c("scale_down", "hold_position"), protect_latex = T) 
```

>>>>

kable(hypothesis_table, col.names = c("Hypotheses and Specific Predictions", "RP", "DP","RP", "DP", "Results"), caption = "Table 1. Table of hypotheses and associated specific predictions, whether each was supported ('yes'; signficant at p<0.05), rejected ('no'; opposite trend signficant at p<0.05), or found insigificant ('n.s.'; no significant correlation), and display items showing the results. 'RP' and 'DP' refer to ring- and diffuse- porous species, respectively.", format = "latex", booktabs = TRUE,  escape = F)%>%
  #column_spec(1, width = "4cm") %>%
  add_header_above(c(" ", "SCBI" = 2, "Harvard"=2, " " )) %>%
  pack_rows("1. Warmer early springs result in earlier stem growth and longer growing seasons", 1, 5, latex_gap_space = "1em", colnum = 4, hline_before = FALSE) %>%
  pack_rows("2. Maximum growth rates are independent of early spring temperatures.", 6, 6, latex_gap_space = "1em", colnum = 4, hline_before = FALSE) %>%
  pack_rows("3. Annual stem growth responds positively to warmer spring temperatures.", 7, 8, latex_gap_space = "1em", colnum = 4, hline_before = FALSE) %>%
  kable_styling(latex_options = c("scale_down", "hold_position"), protect_latex = T) 
```
